# Cross-references {#cross}


```{r, echo=FALSE}
# tomada de:
# http://pj.freefaculty.org/R/WorkingExamples/plot-3d-MVNormal-1.R
library("mvtnorm")

N=50
x <- seq(-3,3, length=N)
y <- seq(-3,3,length=N)
z <- matrix(0, N, N)
for (i in 1:N) for (j in 1:N) {
  z[i,j]=dmvnorm(c(x[i],y[j]), c(0,0),
        matrix(c(1,0.5,0.5,1),2,2))}
 persp(x,y,z,theta=20, phi=15, 
       xlab="x", 
       ylab="y", 
       zlab="f(x,y)",
       scale=TRUE,
       expand=.4,
       axes=TRUE,
       col="#db524f")
```


Cross-references make it easier for your readers to find and link to elements in your book.

## Chapters and sub-chapters

There are two steps to cross-reference any heading:

1. Label the heading: `# Hello world {#nice-label}`. 
    - Leave the label off if you like the automated heading generated based on your heading title: for example, `# Hello world` = `# Hello world {#hello-world}`.
    - To label an un-numbered heading, use: `# Hello world {-#nice-label}` or `{# Hello world .unnumbered}`.

1. Next, reference the labeled heading anywhere in the text using `\@ref(nice-label)`; for example, please see Chapter \@ref(cross). 
    - If you prefer text as the link instead of a numbered reference use: [any text you want can go here](#cross).

## Captioned figures and tables

Figures and tables *with captions* can also be cross-referenced from elsewhere in your book using `\@ref(fig:chunk-label)` and `\@ref(tab:chunk-label)`, respectively.

See Figure \@ref(fig:nice-fig).

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center', fig.alt='Plot with connected points showing that vapor pressure of mercury increases exponentially as temperature increases.'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Don't miss Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(pressure, 10), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```
